---
title: "Constraints on biological condition in the San Gabriel River"
author: "Raphael D. Mazor and Marcus Beck"
date: "November 15, 2017"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
self_contained: yes

---

```{r setup, include=FALSE}
library(ggmap)
library(rgdal)
library(plyr)
knitr::opts_chunk$set(echo = TRUE)
```



## Basemap
This is a basemap of the San Gabriel River watershed, from google maps.
It's a black-and-white satellite view, with a transparent gray rectangle on top, which should make overplotting easier to see.
```{r basemap, echo=FALSE}

load("sgrrmp/data/spatial_data/nhd.sgr.fort.Rdata")
sg.box<-make_bbox(lon=nhd.sgr.fort$long, lat=nhd.sgr.fort$lat, f=0.25)
sg.map<-get_map(location=sg.box, zoom=10, source="google", maptype="satellite", color="bw")
SGbasemap2<-ggmap(sg.map)
SGbasemap2.basemap<-SGbasemap2+ 
  geom_rect(xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, fill="#f0f0f020")+
  coord_map(xlim=c(min(nhd.sgr.fort$long, na.rm=T)-.025,max(nhd.sgr.fort$long, na.rm=T)+.025),
            ylim=c(min(nhd.sgr.fort$lat, na.rm=T)-.025,max(nhd.sgr.fort$lat, na.rm=T)+.025))
SGbasemap2.basemap

```
## Add flowlines
I have the fortified flowlines for the San Gabriel River from NHD+.
```{r add flowlines, echo=F}
SGbasemap2.basemap+
  geom_path(data=nhd.sgr.fort, aes(x=long, y=lat, group=COMID), color="#1f78b4")
```
## Overlay observed scores
I have several sites, with replicates. We will plot the mean CSCI score at each location.

```{r add scores, echo=F}
load("sgrrmp/data/csci.Rdata")
load("sgrrmp/data/sites.Rdata")
load("sgrrmp/data/comid_statewide.Rdata")
csci.d<-ddply(csci, .(StationCode), summarize, csci=max(Result, na.rm=T))
sites.comid<-join(sites, comid)
sites.c<-join(sites.comid, csci.d)
sites.reps<-join(sites.comid,csci[,c("StationCode","SampleDate", "Result")])

n.sites<-length(unique(sites.c$StationCode))
n.samps<-nrow(unique(csci[which(csci$StationCode %in% sites$StationCode), c("StationCode","SampleDate", "FieldSampleID")]))
n.segs<-length(unique(sites.c$COMID))
SGbasemap2.basemap+
 geom_path(data=nhd.sgr.fort, aes(x=long, y=lat, group=COMID), color="#1f78b4")+
  geom_point(data=sites.c[!is.na(sites.c$csci),], aes(x=ActualLongitude, y=ActualLatitude,
                              fill=csci), size=3, shape=21)+
 scale_fill_gradient2(name="Observed score", high="#2c7bb6", mid="#abd9e9", low="#d7191c", midpoint = 0.79)

print(paste(c("There are",n.samps,"sampling events from",n.sites,"unique locations on",n.segs,"unique stream-segments"), collapse=" "))
```
So let's add context: 
Here are flow-lines colored by likely score
```{r likely score map}
SGbasemap2.basemap+
 geom_path(data=nhd.sgr.fort, aes(x=long, y=lat, group=COMID, color=full0.50) )+
  # geom_point(data=sites.c[!is.na(sites.c$csci),], aes(x=ActualLongitude, y=ActualLatitude,
  #                             fill=csci), size=3, shape=21)+
 scale_color_gradient2(name="Observed score", high="#2c7bb6", mid="#abd9e9", low="#d7191c", midpoint = 0.79)
``