---
title: "Constraints on biological condition in the San Gabriel River"
author: "Raphael D. Mazor and Marcus Beck"
date: "November 15, 2017"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
self_contained: yes

---

```{r setup, include=FALSE}
library(ggmap)
library(rgdal)
library(plyr)
knitr::opts_chunk$set(echo = TRUE, warnings=FALSE)
```

## CSCI scores in the SGRRMP
```{r csci_scores, echo=F,fig.height=10}
load("data/csci.Rdata")
load("data/sites.Rdata")
load("data/comid_statewide.Rdata")
csci.d<-ddply(csci, .(StationCode), summarize, csci=max(Result, na.rm=T))
sites.comid<-join(sites, comid)
sites.c<-join(sites.comid, csci.d)
sites.reps<-join(sites.comid,csci[,c("StationCode","SampleDate", "Result")])


sites.c<-sites.c[order(sites.c$full0.50),]
sites.c$StationCode<-factor(sites.c$StationCode, levels=sites.c$StationCode)
scores.plot<-
  ggplot(data=sites.c, aes(x=StationCode, y=csci))+
  geom_point(shape=21, size=2, fill="white")+
  theme_classic()+
  ylab("CSCI score")+
  coord_flip()
scores.plot

n.sites<-length(unique(sites.c$StationCode))
n.samps<-nrow(unique(csci[which(csci$StationCode %in% sites$StationCode), c("StationCode","SampleDate", "FieldSampleID")]))
n.segs<-length(unique(sites.c$COMID))

print(paste(c("There are",n.samps,"sampling events from",n.sites,"unique locations on",n.segs,"unique stream-segments"), collapse=" "))
```
Add threshold:
```{r thresh,echo=F,fig.height=10}
scores.plot+
  geom_hline(yintercept=0.79, linetype="dashed")
```

Add predicted range:
```{r range, echo=F,fig.height=10}
sel.sites<-unique(sites.c$StationCode)
plot.dat_1site<-
  unique(sites.reps[which(sites.reps$StationCode %in% sel.sites),
             c("StationCode",
               "full0.05","full0.10","full0.15","full0.20","full0.25","full0.30","full0.35","full0.40","full0.45","full0.50","full0.55","full0.60","full0.65","full0.70","full0.75","full0.80","full0.85","full0.90","full0.95",
"full.class")])

plot.dat_1site<-plot.dat_1site[order(plot.dat_1site$full0.50),]
plot.dat_1site$StationCode<-factor(plot.dat_1site$StationCode, levels=plot.dat_1site$StationCode)

range.plot<-ggplot(data=plot.dat_1site, aes(x=StationCode, y=full0.50))+
  # geom_point(shape=21, size=2, fill="white")+
  geom_linerange(aes(ymin=full0.05, ymax=full0.95), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.10, ymax=full0.90), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.15, ymax=full0.85), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.20, ymax=full0.80), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.25, ymax=full0.75), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.30, ymax=full0.70), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.35, ymax=full0.65), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.40, ymax=full0.60), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.45, ymax=full0.55), size=4, alpha=0.11)+
  theme_classic()+
  coord_flip()+
  ylab("CSCI score")+
  geom_hline(yintercept=0.79, linetype="dashed")
range.plot
```
Add classifications
```{r classes_sites, echo=F, fig.height=10, warnings=FALSE}

range.class<-
  ggplot(data=plot.dat_1site, aes(x=StationCode, y=full0.50))+
  # geom_point(shape=21, size=2, fill="white")+
  geom_linerange(aes(ymin=full0.05, ymax=full0.95, color=full.class), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.10, ymax=full0.90, color=full.class), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.15, ymax=full0.85, color=full.class), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.20, ymax=full0.80, color=full.class), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.25, ymax=full0.75, color=full.class), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.30, ymax=full0.70, color=full.class), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.35, ymax=full0.65, color=full.class), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.40, ymax=full0.60, color=full.class), size=4, alpha=0.11)+
  geom_linerange(aes(ymin=full0.45, ymax=full0.55, color=full.class), size=4, alpha=0.11)+
  theme_classic()+
  coord_flip()+
  geom_hline(yintercept=0.79, linetype="dashed")+
  ylab("CSCI score")+
  scale_color_manual(name="Stream Class",values=c("#fb9a99","#a6cee3","#b2df8a"),
                     labels=c("Likely constrained","Likely high quality","Intermediate or\nindeterminate"))+
  guides(colour = guide_legend(override.aes = list(alpha=1)))

range.class
```

## Basemap
This is a basemap of the San Gabriel River watershed, from google maps.
It's a black-and-white satellite view, with a transparent gray rectangle on top, which should make overplotting easier to see.
```{r basemap, echo=FALSE,fig.height=8}

load("data/spatial_data/nhd.sgr.fort.Rdata")
sg.box<-make_bbox(lon=nhd.sgr.fort$long, lat=nhd.sgr.fort$lat, f=0.25)
sg.map<-get_map(location=sg.box, zoom=10, source="google", maptype="satellite", color="bw")
SGbasemap2<-ggmap(sg.map)
SGbasemap2.basemap<-SGbasemap2+ 
  geom_rect(xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, fill="#f0f0f020")+
  coord_map(xlim=c(min(nhd.sgr.fort$long, na.rm=T)-.025,max(nhd.sgr.fort$long, na.rm=T)+.025),
            ylim=c(min(nhd.sgr.fort$lat, na.rm=T)-.025,max(nhd.sgr.fort$lat, na.rm=T)+.025))
SGbasemap2.basemap

```
## Add flowlines
I have the fortified flowlines for the San Gabriel River from NHD+.
```{r add flowlines, echo=F,fig.height=8}
SGbasemap2.basemap+
  geom_path(data=nhd.sgr.fort, aes(x=long, y=lat, group=COMID), color="#1f78b4")
```
## Overlay observed scores
I have several sites, with replicates. We will plot the mean CSCI score at each location.

```{r add scores, echo=F,fig.height=8}
SGbasemap2.basemap+
 geom_path(data=nhd.sgr.fort, aes(x=long, y=lat, group=COMID), color="#1f78b4")+
  geom_point(data=sites.c[!is.na(sites.c$csci),], aes(x=ActualLongitude, y=ActualLatitude,
                              fill=csci), size=3, shape=21)+
 scale_fill_gradient2(name="Observed score", high="#2c7bb6", mid="#abd9e9", low="#d7191c", midpoint = 0.79)


```
So let's add context: 
Here are flow-lines colored by likely score
```{r likely score map, echo=FALSE,fig.height=8}
SGbasemap2.basemap+
 geom_path(data=nhd.sgr.fort, aes(x=long, y=lat, group=COMID, color=full0.50) )+
  # geom_point(data=sites.c[!is.na(sites.c$csci),], aes(x=ActualLongitude, y=ActualLatitude,
  #                             fill=csci), size=3, shape=21)+
 scale_color_gradient2(name="Likely score", high="#2c7bb6", mid="#abd9e9", low="#d7191c", midpoint = 0.79)
```
